Supermassive black holes and their host spheroids \\ III. A universal $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation

### 2015-12-04 papers/mbhn/mbhn.tex
friday stereosonics

\title{Supermassive black holes and their host spheroids \\ 
III. A universal $M_{\rm BH} - n_{\rm sph}$ correlation }

@@

\begin{abstract}
The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, has been shown to tightly correlate 
with the mass of the central supermassive black hole, $M_{\rm BH}$. 
The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations 
involving the spheroid luminosity, $L_{\rm sph}$: 
the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ correlations.

However, obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of the galaxy's light distribution 
and some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation.

With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
and other black hole mass scaling relations, 
we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
In this paper, the third of its series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
they reunite into a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
with relatively small intrinsic scatter ($\epsilon_{(M_{\rm BH} | n_{\rm sph})} \simeq 0.25 \rm~dex$). 
{\bf to be finished...}
\end{abstract}

\keywords{keywords}

@@

I(R; I_{\rm e},R_{\rm e},n) = I_{\rm e} \exp \biggl \{ -b_{\rm n} \biggl [ \Bigl (\frac{R}{R_{\rm e}} \bigr )^{1/n} -1 \biggr ] \biggr \}, 

@@

and $b_{\rm n}$ is a constant defined in terms of the S\'ersic index $n$ (see \citealt{grahamdriver2005}, and references therein). 

@@

and still regained a significant $M_{\rm BH} - n_{\rm sph}$ relation. 

@@

between the black hole mass and several galaxy structural parameters, 
we performed state-of-the-art modelling for the largest sample of galaxies to date (\citealt{paperI}, hereafter \emph{Paper I}),  

@@

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample used in \emph{Paper II} (and presented here in Table \ref{tab:sample}), 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
\cite{ellicular} demonstrate that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices were estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by other studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes, which report only the statistical errors 
associated with their fitted parameters. 
Readers should refer to \emph{Paper I} for a more detailed discussion on this topic. }. 
For this analysis, we elected to use the spheroid S\'ersic indices obtained from the decomposition of the one-dimensional 
major-axis surface brightness profiles of our galaxies.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes the two galaxies classified as E/S0, 
whereas the two galaxies classified as S0/Sp and the two galaxies classified as ``mergers'' are included in neither the early- nor the late-type bin.

@@

\section{Analysis and results}
\label{sec:anal}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
\cite{tremaine2002} cautioned that 
the BCES estimator becomes ineffective when the dataset contains at least one low-precision measurement -- 
regardless of how many high-precision measurements are in the sample -- 
and tends to be biased in case of low number statistics 
or if the mean square of the uncertainties associated to the independent variable is comparable to 
the variance of the distribution of the independent variable. 
According to the results from the Monte Carlo Markov Chain simulations of \cite{tremaine2002} and \cite{novak2006}, 
these problems can be overcome with the use of the modified FITEXY routine. 
\cite{park2012} also concluded that the modified FITEXY routine performs better and returns less biased results than the BCES estimator, 
and noted that the the modified FITEXY routine is computationally less intensive than the Bayesian technique {\tt linmix\_err}. 
Given that at least one of our subsamples (the lenticular galaxies) has a small size 
and that the uncertainties associated to $n_{\rm sph}$ are relatively large 
compared to the range spanned by the $n_{\rm sph}$ values for most of our subsamples, 
we put more trust in the results obtained with the modified FITEXY routine 
and throughout the text we quote only those. \\ 
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict the value of the observable $Y$ with the best possible precision. \\
We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
the lenticular galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
These two galaxies have therefore been excluded from the rest of the analysis.

@@

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevented us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
%($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
%and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we know that the early-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{1.03 \pm 0.11}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
this prediction is in excellent agreement with the observed slope of $3.58 \pm 0.27$ obtained here. 
On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$, 
from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
this is consistent with the observed slope of $4.55 \pm 0.66$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph} - 0.50 \bigr) . 
\end{equation*}
\\

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lregMn} 
\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $L_{\rm sph}$ direction. 
The lenticular galaxies NGC 0524 and NGC 3998 were excluded from the linear regression analysis (see Section \ref{sec:anal}). 
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2).  }
\end{table*}

@@

%%
\acknowledgments
GS warmly thanks Alister Graham and Carlo Nipoti for useful discussion. 
%We also thank the anonymous referee for useful comments and suggestions. 
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration. 
We acknowledge the usage of the HyperLeda database (\url{http://leda.univ-lyon1.fr}).
The BCES routine \citep{akritasbershady1996} was run via the python module 
written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.

>>>>

\title{Supermassive black holes and their host spheroids \\ 
III. A universal $M_{\rm BH} - \lowercase{n_{\rm sph}}$ correlation }

@@

\begin{abstract}
The S\'ersic $R^{1/n}$ model is the best approximation known to date for describing the light distribution of stellar spheroidal and disk components, 
with the S\'ersic index $n$ providing a direct measure of the central radial concentration of stars. 
The S\'ersic index of a galaxy's spheroidal component, $n_{\rm sph}$, has been shown to tightly correlate 
with the mass of the central supermassive black hole, $M_{\rm BH}$. 
The $M_{\rm BH} - n_{\rm sph}$ correlation is also expected from other two well known scaling relations 
involving the spheroid luminosity, $L_{\rm sph}$: 
the $L_{\rm sph} - n_{\rm sph}$ and the $M_{\rm BH} - L_{\rm sph}$ correlations. 
Obtaining an accurate estimate of the spheroid S\'ersic index requires a careful modelling of a galaxy's light distribution 
and some studies have failed to recover a statistically significant $M_{\rm BH} - n_{\rm sph}$ correlation. 
With the aim of re-investigating the $M_{\rm BH} - n_{\rm sph}$ 
and other black hole mass scaling relations, 
we performed a detailed (i.e.~bulge, disks, bars, spiral arms, rings, halo, nucleus, etc.) 
decomposition of 66 galaxies, with directly measured black hole masses, 
that had been imaged at $3.6\rm~\mu m$ with \emph{Spitzer}. 
In this paper, the third of its series, we present an analysis of the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams. 
While early-type (elliptical+lenticular) and late-type (spiral) galaxies split into two separate relations 
in the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
they reunite into a single $M_{\rm BH} \propto n_{\rm sph}^{3.39 \pm 0.15}$ sequence
with relatively small intrinsic scatter ($\epsilon_{(M_{\rm BH} | n_{\rm sph})} \simeq 0.25 \rm~dex$). 
The black hole mass is therefore closely related to the spheroid central concentration of stars, 
which mirrors the inner gradient of the spheroid gravitational potential. 
\end{abstract}

\keywords{black hole physics; galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure}

@@

I(R; I_{\rm e},R_{\rm e},n) = I_{\rm e} \exp \biggl \{ -b_{\rm n} \biggl [ \biggl (\frac{R}{R_{\rm e}} \biggr )^{1/n} -1 \biggr ] \biggr \}, 

@@

and $b_{\rm n}$ is a constant defined in terms of the S\'ersic index (see \citealt{grahamdriver2005}, and references therein). 

@@

and still regained a significant $M_{\rm BH} - n_{\rm sph}$ correlation. 

@@

between the black hole mass and several host spheroid structural parameters, 
we performed state-of-the-art modelling for the largest sample of galaxies to date (\citealt{paperI}, hereafter \emph{Paper I})  

@@

\section{Data}
We populated the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams 
with the same galaxy sample used in \emph{Paper II} (and presented here in Table \ref{tab:sample}), 
i.e.~66 galaxies for which a dynamical measurement of the black hole mass has been reported in the literature 
(by \citealt{grahamscott2013} or \citealt{rusli2013}) 
and for which we were able to successfully model the light distribution and measure the spheroid structural parameters 
using $3.6\rm~\mu m$ \emph{Spitzer} satellite images. 
Our galaxy decompositions take into account bulge, disks, spiral arms, bars, rings, halo, 
extended or unresolved nuclear source and partially depleted core, 
and -- for the first time -- they were checked to be consistent with the galaxy kinematics 
\citep{atlas3dIII,scott2014,arnold2014}. 
Kinematical information was used to confirm the presence of disk components 
in the majority of early-type (elliptical + lenticular) galaxies and, more importantly,  
to estabilish the radial extent of these disks, 
which in most cases is not obvious from a visual inspection of the galaxy images. 
This enabled us to distinguish between intermediate-scale disks, 
that are fully embedded in the spheroid,  
and large-scale disks, that encase the bulge and dominate the light at large radii.  
\cite{ellicular} demonstrate that when an intermediate-scale disk is misclassified and modeled as a large-scale disk, 
the luminosity of the spheroid is underestimated, 
hence the galaxy incorrectly appears as a positive outlier (an ``over-massive'' black hole) in the $M_{\rm BH} - L_{\rm sph}$ diagram. 
A detailed description of the dataset used here, the data reduction process and the galaxy modelling technique that we developed 
can be found in \emph{Paper I}, 
along with a discussion of how we estimated the uncertainties on the spheroid S\'ersic indices\footnote{The uncertainties associated with 
the spheroid S\'ersic indices were estimated with a method that takes into account systematic errors. 
This method consists in comparing, for each of our galaxies, the measurements of the spheroid S\'ersic index obtained by other studies 
with that obtained by us. 
Systematic errors are typically not considered by popular 2D fitting codes, which report only the statistical errors 
associated with their fitted parameters. 
Readers should refer to \emph{Paper I} for a more detailed discussion on this topic. }. 
For the present analysis, we elected to use the spheroid S\'ersic indices obtained from the decomposition of the one-dimensional 
major-axis surface brightness profiles of our galaxies.  
The morphological classification (E = elliptical; E/S0 = elliptical/lenticular; S0 = lenticular; 
S0/Sp = lenticular/spiral; Sp = spiral; and ``merger'') follows from the galaxy decompositions illustrated in \emph{Paper I}. 
As in \emph{Paper II}, we will refer to early-type galaxies (E+S0) and late-type galaxies (Sp). 
The early-type bin includes the two galaxies classified as E/S0, 
whereas the two galaxies classified as S0/Sp and the two galaxies classified as ``mergers'' are included in neither the early- nor the late-type bin.

@@

\section{Analysis and results}
\label{sec:anal}
As in \emph{Paper II}, a linear regression analysis of the $L_{\rm sph} - n_{\rm sph}$ 
(Table \ref{tab:lregLn} and Figure \ref{fig:magn})
and $M_{\rm BH} - n_{\rm sph}$ (Table \ref{tab:lregMn} and Figure \ref{fig:mbhn}) diagrams 
was performed using three different routines: 
the BCES code from \cite{akritasbershady1996}, 
the FITEXY routine \citep{press1992}, as modified by \cite{tremaine2002}, 
and the Bayesian estimator {\tt linmix\_err} \citep{linmixerr}.
All of these three routines take into account the intrinsic scatter, 
but only the FITEXY and the {\tt linmix\_err} codes allow one to quantify it.
\cite{tremaine2002} cautioned that 
the BCES estimator becomes ineffective when the dataset contains at least one low-precision measurement -- 
regardless of how many high-precision measurements are in the sample -- 
and tends to be biased in case of low number statistics, 
or if the mean square of the uncertainties associated to the independent variable is comparable to 
the variance of the distribution of the independent variable. 
According to the results from the Monte Carlo Markov Chain simulations of \cite{tremaine2002} and \cite{novak2006}, 
these problems can be overcome with the use of the modified FITEXY routine. 
\cite{park2012} also concluded that the modified FITEXY routine performs better and returns less biased results than the BCES estimator, 
and noted that the the modified FITEXY routine is computationally less intensive than the Bayesian technique {\tt linmix\_err}. 
Given that at least one of our subsamples (the lenticular galaxies) has a small size 
and that the uncertainties associated to $n_{\rm sph}$ are relatively large 
compared to the range spanned by the $n_{\rm sph}$ values for most of our subsamples, 
we put more trust in the results obtained with the modified FITEXY routine 
and throughout the text we quote only those. \\ 
We report both symmetrical and nonsymmetrical linear regressions.  
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas nonsymmetrical forward ($Y|X$) regressions -- which minimize the scatter in the $Y$ direction -- 
allow one to predict the value of the observable $Y$ with the best possible precision. \\
We searched for extreme outliers in both the $L_{\rm sph} - n_{\rm sph}$ and $M_{\rm BH} - n_{\rm sph}$ diagrams, 
and found that in our $L_{\rm sph} - n_{\rm sph}$ plot there are no $3\sigma$ outliers, 
whereas in our $M_{\rm BH} - n_{\rm sph}$ plot 
the lenticular galaxies NGC 0524 and NGC 3998 reside more than $3\sigma$ from the bisector linear regression for all galaxies. 
These two galaxies have therefore been excluded from the rest of the analysis.

@@

\subsection{$M_{\rm BH} - n_{\rm sph}$}
\cite{grahamscott2013} presented two different $M_{\rm BH} - L_{\rm sph}$ relations for S\'ersic and core-S\'ersic 
spheroids\footnote{Core-S\'ersic spheroids have partially depleted cores relative to their outer S\'ersic light profile, 
whereas S\'ersic spheroids have no central deficit of stars. } \citep{graham2003coresersicmodel,trujillo2004coresersicmodel}.
However, in \emph{Paper II} we found that the slopes of the $M_{\rm BH} - L_{\rm sph}$ correlations for S\'ersic and core-S\'ersic spheroids 
are consistent with each other within their $1\sigma$ uncertainties, 
which prevented us from considering them as two separate sequences. 
On the other hand, our analysis showed that early- and late-type galaxies follow two different $M_{\rm BH} - L_{\rm sph}$ relations. 
%($M_{\rm BH} \propto L_{\rm sph}^{1.00 \pm 0.10}$ 
%and $M_{\rm BH} \propto L_{\rm sph}^{2.88 \pm 0.68}$, respectively). \\
Given that early- and late-type galaxies define two separate sequences in both the $L_{\rm sph} - n_{\rm sph}$ 
and $M_{\rm BH} - L_{\rm sph}$ diagrams, 
we investigate substructure in the $M_{\rm BH} - n_{\rm sph}$ diagram. 
Using the results from the modified FITEXY routine, 
we know that the early-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{1.03 \pm 0.11}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{3.60 \pm 0.19}$, 
therefore we expect to find $M_{\rm BH} \propto n_{\rm sph}^{3.69 \pm 0.44}$; 
this prediction is in excellent agreement with the observed log-slope of $3.58 \pm 0.27$ obtained here. 
On the other hand, late-type galaxies follow $M_{\rm BH} \propto L_{\rm sph}^{2.58 \pm 1.06}$ 
and $L_{\rm sph} \propto n_{\rm sph}^{1.44 \pm 0.52}$, 
from which one can predict $M_{\rm BH} \propto n_{\rm sph}^{3.72 \pm 2.03}$; 
this is consistent with the observed log-slope of $4.55 \pm 0.66$. 
The Bayesian estimator {\tt linmix\_err} returns consistent results: 
a slope of $3.44 \pm 0.33$ for the early-type galaxies 
and a slope of $4.12 \pm 1.07$ for the late-type galaxies. 
In both cases, the values of the slope and intercept for the early- and late-type galaxies 
are consistent with each other within their $1\sigma$ uncertainties\footnote{In effect, 
considering the results of the modified FITEXY routine, 
the slopes of the relations for early- and late-type galaxies 
are only marginally consistent with each other within their $1\sigma$ uncertainties. 
However, the same slopes obtained with Bayesian estimator {\tt linmix\_err} 
are fully consistent with each other within their $1\sigma$ uncertainties. }.
Our analysis shows that the early- and late-type galaxies do not follow two separate trends in the $M_{\rm BH} - n_{\rm sph}$ diagram, 
i.e.~we do not identify any significant substructure based on the galaxy morphological type. \\
The symmetrical linear regression for all galaxies obtained with the modified FITEXY routine is: 
\begin{equation*}
\log \biggl( \frac{M_{\rm BH}}{\rm M_\odot} \biggr) = (8.15 \pm 0.06) + (3.37 \pm 0.15) \bigl(\log n_{\rm sph} - 0.50 \bigr) . 
\end{equation*}
\\

@@

\tableline 
\tableline
\end{tabular}
\label{tab:lregMn} 
\tablecomments{For each subsample, we indicate $\langle \log n_{\rm sph} \rangle$, its average value of spheroid S\'ersic index. 
In the last two columns, we report $\epsilon$, the intrinsic scatter, and $\Delta$, the total rms scatter in the $M_{\rm BH}$ direction. 
The lenticular galaxies NGC 0524 and NGC 3998 were excluded from the linear regression analysis (see Section \ref{sec:anal}). 
Both the early- and late-type subsamples do not contain the two galaxies classified as S0/Sp and the two galaxies classified as mergers (45+17=66-2-2).  }
\end{table*}

@@

%%
\acknowledgments
GS warmly thanks Alister Graham and Carlo Nipoti for useful discussion. 
%We also thank the anonymous referee for useful comments and suggestions. 
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration. 
We acknowledge the usage of the HyperLeda database (\url{http://leda.univ-lyon1.fr}).
The BCES routine \citep{akritasbershady1996} was run via the python module 
written by Rodrigo Nemmen \citep{nemmen2012}, which is available at \url{https://github.com/rsnemmen/BCES}.
The modified FITEXY linear regressions were performed using the IDL routine MPFITEXY \citep{williams2010}, 
which is available at \url{http://purl.org/mike/mpfitexy}. 
The MPFITEXY routine depends on the MPFIT package \citep{markwardt2009}.
